\section{Conclusion}

This paper presented RoCBF-Net, a tunable safety filtering architecture that integrates HOCBF constraints, GP residual learning, and a scalar robustness factor $\epsilon_\kappa$. The central empirical finding is that $\epsilon_\kappa$ should be treated as a commissioning-calibrated parameter---not a fixed theoretical constant---whose optimal value depends systematically on the uncertainty type and coupling strength.

Four results support this conclusion. \textbf{(1)} On a 5th-order supercritical boiler-turbine benchmark under $\Phi$-scaled nonlinear dynamics with eight conditions, GP mean correction alone ($\epsilon_\kappa=0$) reduces HOCBF violations by $>500\times$ (from $>99\%$ to $\leq0.18\%$) on six of seven uncertainty scenarios, establishing GP learning---not the compositional $\epsilon(x)$ margin---as the dominant safety mechanism. \textbf{(2)} An $\epsilon_\kappa$ sensitivity sweep reveals that $\epsilon_\kappa=0$ suffices for additive perturbations, while $\epsilon_\kappa=0.1$ restores zero-violation safety under state-dependent coupling (S3, 33.5\% $\to$ 0.00\%); $\epsilon_\kappa=1.0$ is never the optimal choice under any tested condition and underperforms the best calibrated $\kappa$. \textbf{(3)} A coupling-strength gradient experiment across $\gamma\in\{0.5,1.0,1.5,2.0\}$ uncovers a \emph{deployment envelope}: the safe $\epsilon_\kappa$ range shrinks from $[0.1,1.0]$ at weak coupling to $[0.1,0.5]$ at medium coupling, and collapses to $\{0\}$ at strong coupling ($\gamma\geq1.5$), where any positive margin constrains the QP without providing protection. \textbf{(4)} With correct calibration, the GP-HOCBF filter matches NMPC on safety ($\leq$0.18\% vs.\ $\leq$0.08\% violation) at approximately one-tenth the computational cost (${\sim}25$\,ms vs.\ 254\,ms per step).

The method is intended as a commissioning-calibrated safety filter: characterize the target uncertainty regime during commissioning (GP pretraining on scenario-representative data), then select $\epsilon_\kappa$ according to the perturbation structure and coupling strength. The deployment envelope established here defines the regime in which $\epsilon_\kappa$ is useful ($0.5\leq\gamma<1.5$), and identifies the regime ($\gamma\geq1.5$) where it must be set to zero and QP infeasibility used as a diagnostic for fallback. Future work includes extending to matched uncertainty ($\Delta g \neq 0$), developing principled OOD detection for GP-based safety filters, and validation on higher-fidelity industrial simulators.
