\section{Conclusion}
\label{sec:conclusion}

This paper presented RoCBF-Net as a tunable GP-HOCBF safety filter for a 1000\,MW ultra-supercritical boiler-turbine measurement and control loop. The filter sits between an upstream controller and the actuators, using measured pressure, enthalpy, power, fuel, and delay states to project the proposed action into the process-safe set.

The main engineering conclusion is that robustness margins should be commissioned, not fixed. On the 5th-order nonlinear CCS benchmark with $\Phi$-scaled control effectiveness, GP mean correction alone reduces HOCBF violations by more than 500 times and achieves $\leq0.18\%$ violation in six of seven uncertainty scenarios. For additive perturbations, the recommended setting is $\epsilon_\kappa=0$ because GP mean correction provides the useful compensation and the margin mainly reduces QP feasibility. For moderate state-dependent coupling, $\epsilon_\kappa=0.1$ restores zero violation where the GP-only filter fails. The full theoretical setting $\epsilon_\kappa=1.0$ is not preferred in any tested condition because it can over-constrain the QP and trigger fallback. The coupling-strength sweep defines the deployment envelope: small positive margins are useful for $0.5\leq\gamma<1.5$, while beyond $\gamma\geq1.5$ the margin should be disabled and infeasibility should be treated as a fallback or alarm signal.

The computational result supports real-time use in the simulated DCS loop. The JIT-compiled GP-HOCBF-QP pipeline runs at about 25\,ms per step on an RTX 4090 GPU, within the 1\,s sampling budget and approximately ten times faster than the implemented SLSQP-based NMPC benchmark. This timing comparison is against the implemented research NMPC baseline, not against optimized proprietary industrial MPC packages.

The validation boundary should guide use of the results. All evidence is from simulation benchmark experiments rather than plant trials, so the commissioning schedule is a pre-deployment validation protocol rather than a field authorization. The model-mismatch formulation assumes $\Delta g=0$, so actuator-gain uncertainty and severe valve nonlinearities require additional treatment. The invariance result is continuous-time and probabilistic, while the implemented controller is sampled-data with zero-order hold; inter-sample behavior is checked empirically, but a formal discrete-time invariance theorem is not claimed. The next validation steps are hardware-in-the-loop testing, plant historian calibration, actuator-gain uncertainty, and certified sampled-data GP-HOCBF filtering.
