\section{Introduction}

\subsection{Industrial Measurement and Control Context}

Supercritical thermal power units---the backbone of modern electricity generation---operate at main steam pressures exceeding 22\,MPa and temperatures above 600$^\circ$C. Safe operation requires continuous measurement and constraint-preserving control of three critical process variables: main steam pressure, separator outlet enthalpy, and turbine power output. These constraints originate from multiple layers of the industrial control architecture: sensor measurement ranges, actuator saturation limits, equipment protection boundaries, and coordinated control requirements.

During daily operation, the nominal plant model diverges from reality. Coal quality fluctuates across shipments, heat exchanger surfaces foul progressively, and actuators degrade over months of service. These factors introduce persistent model mismatch between the design model used for controller synthesis and the true plant dynamics. Under such mismatch, a controller---whether classical PID, model predictive control (MPC), or a learned policy---may issue control actions that appear safe under the nominal model but violate physical constraints on the actual plant.

\subsection{The Safety Layer Approach}

Rather than modifying or replacing the upstream controller, we adopt a \emph{safety layer} architecture: an independent measurement-and-control safety filter that sits between any upstream controller and the plant actuators. The filter receives the controller's proposed action $u_{\mathrm{prop}}$, evaluates it against the current plant measurements and a calibrated model of the dynamics, and projects it to the nearest action $u^*$ that is certified safe. This architecture has two practical advantages for industrial deployment: (i)~it does not require modification of existing control logic, and (ii)~the safety guarantee is independent of the upstream controller type---LQR, MPC, PID, or a trained policy all receive the same protection.

The technical mechanism for this projection is the control barrier function (CBF)~\cite{ames2017cbf}, which enforces forward invariance of a safe set through a quadratic program (QP) solved at each measurement sample. For industrial process variables with high relative degree---steam pressure requires two Lie derivatives of the constraint function to reach the control input---high-order CBFs (HOCBFs)~\cite{xiao2021hocbf} extend this construction through a recursive $\psi$-chain. The fundamental limitation is that under model mismatch, the HOCBF constraint is computed from incorrect dynamics, and the QP may certify an unsafe action as safe.

\subsection{Technical Gap: Uncertainty Propagation in High-Relative-Degree Constraints}

Gaussian processes (GPs) learn model residuals from measurement data with calibrated uncertainty quantification~\cite{rasmussen2006gp,srinivas2010gp}. Several works combine GPs with CBFs for robust safety~\cite{cheng2019guaranteed,fisac2018general}, but apply the GP uncertainty only at the top CBF level ($m=1$). A recent concurrent work~\cite{aali2024learning} extends this to HOCBFs via SOCP chance-constraint reformulation, providing a convex safety filter---but the reformulation is global rather than recursive, aggregating uncertainty at the constraint level rather than through each $\psi$-level individually. For industrial constraints with $m\geq 2$, this is structurally significant: the model residual propagates through successive Lie derivatives of the constraint function, and the uncertainty amplifies through each level of the $\psi$-chain. Our compositional $\sigma$-chain captures this per-level amplification by propagating per-dimension GP posterior uncertainties recursively, yielding a per-constraint, state-dependent robustness margin $\epsilon(x)$ that more precisely reflects the uncertainty structure at each relative-degree level. Similarly, cautious MPC~\cite{hewing2020cautious} propagates GP uncertainty through a prediction horizon but at substantially higher computational cost and without per-step forward-invariance certification.

\subsection{Contributions}

We introduce an industrial measurement-and-control safety filtering framework based on Robust HOCBF with three contributions:

\begin{enumerate}
    \item \textbf{Real-time safety filtering architecture for industrial measurement and control systems.} The filter operates as an independent safety layer between any upstream controller (LQR, MPC, PID, or learned policy) and the plant actuators, projecting proposed actions to certified-safe actions via a quadratic program solved at each measurement sample. Per-step latency is ${\sim}25$\,ms (GPU, JIT-compiled), compatible with industrial DCS sampling rates. We provide explicit QP feasibility conditions, characterize the one-sided diagnostic limitation of QP infeasibility as a GP calibration indicator, and empirically verify inter-sample constraint satisfaction under zero-order-hold implementation. The guarantee is controller-agnostic: LQR, PPO, and classical controllers all receive the same safety certificate.

    \item \textbf{Compositional GP uncertainty propagation for high-order barrier constraints.} A recursive $\sigma$-chain aggregates per-dimension GP posterior uncertainties across all $m$ relative-degree levels, yielding a per-constraint, state-dependent robustness margin $\epsilon(x)$. Under a fixed scenario-calibrated GP with $\kappa_\epsilon=1$, Theorem~1 establishes forward invariance with probability $\geq 1-\delta$.

    \item \textbf{Supercritical power plant benchmark validation under model mismatch.} Under $\Phi$-scaled nonlinear dynamics with six CBF inequality constraints covering three measured process variables (pressure, enthalpy, power) and six static perturbation scenarios (coal quality drift, pump cycling, coupled state-dependent disturbance, nonlinear fouling, valve degradation, fuel quality variation), Robust HOCBF transforms nominal HOCBF failure ($>95\%$ violation) to no observed CBF violations across all scenarios (5 seeds, 50 evaluation episodes, 95\% Wilson upper bound 1.51\%).
\end{enumerate}

