\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{hyperref}

\title{Cover Letter}
\date{}

\begin{document}

\noindent\textbf{To:} The Editor-in-Chief\\
Journal of Process Control\\[1em]

\noindent\textbf{From:}\\
Zhuang~Shao$^{1,*}$ (Corresponding author), Lijun~Lei$^{2}$, Peng~Wang$^{3}$, Liang~Zheng$^{2}$, Jie~Zhou$^{2}\\[0.5em]
$^{1}$China Resources Power Technology Research Institute Co., Ltd., Shenzhen 518000, China\\
$^{2}$Rundian Energy Science and Technology Co., Ltd., Zhengzhou 450052, China\\
$^{3}$North China University of Water Resources and Electric Power, Zhengzhou 450046, China\\[1em]

\noindent\textbf{Re:} Submission of manuscript\\
``\emph{Robust High-Order Control Barrier Function Safety Filtering for Supercritical Power Plant Control under Model Mismatch}''\\[1em]

\noindent Dear Editor,

We submit the enclosed manuscript for consideration at the Journal of Process Control. The paper introduces a Robust High-Order Control Barrier Function (Robust HOCBF) safety filter that combines Gaussian process mean correction with compositional uncertainty propagation through the HOCBF $\psi$-chain, providing a per-constraint, relative-degree-aware safety certificate for energy process control under model mismatch.

The contribution is a process-control-oriented safety filter: the GP-corrected drift reduces the residual perturbation, and a recursive $\sigma$-chain certifies the remaining uncertainty through a GP confidence-bound-based high-probability forward-invariance guarantee. The filter is policy-agnostic---compatible with LQR, MPC, or learned upstream controllers---and is validated on a 5th-order supercritical boiler-turbine benchmark with $\Phi$-scaled nonlinear dynamics and six CBF-enforceable constraints.

\textbf{Fit with Journal of Process Control.} The manuscript addresses constraint satisfaction in energy process control under model mismatch, a core concern of the journal's scope. The Robust HOCBF filter is proposed as a complement to existing process control techniques (MPC, offset-free MPC, disturbance-observer-based control). The paper includes process-control-specific content: IAE performance metrics, sampled-data implementation analysis, QP feasibility diagnostics, deployment decision guidance, and discussion of practical limitations including scenario-specific GP calibration and the $\Delta g = 0$ assumption.

\textbf{Key contributions:}
\begin{enumerate}
  \item Compositional GP uncertainty propagation through the HOCBF $\psi$-chain, yielding a per-constraint, relative-degree-aware robustness margin with a formal high-probability safety certificate (Theorem~1).
  \item Process-control-oriented safety certification with sampled-data implementation analysis, QP feasibility conditions, and one-sided diagnostic characterization.
  \item Validation on a 5th-order supercritical boiler-turbine benchmark: nominal HOCBF fails catastrophically ($>95\%$ violation) under model mismatch; the Robust HOCBF achieves no observed CBF violations across six static perturbation scenarios with per-step QP latency ${\sim}25$\,ms (10$\times$ faster than the implemented SLSQP-based NMPC baseline).
\end{enumerate}

\textbf{Conflicts of interest.} The authors declare no competing interests. The manuscript has not been published elsewhere and is not under simultaneous consideration by any other journal.

\textbf{Suggested reviewers:}
\begin{itemize}
  \item Prof.\ Melanie N.\ Zeilinger, ETH Zurich, \href{mailto:mzeilinger@ethz.ch}{mzeilinger@ethz.ch} (safe learning-based control, GP-MPC)
  \item Prof.\ Lukas Hewing, University of Oxford, \href{mailto:lukas.hewing@eng.ox.ac.uk}{lukas.hewing@eng.ox.ac.uk} (cautious MPC, GP for control)
  \item Jianxin Zhou, Southeast University, \href{mailto:zjx@seu.edu.cn}{zjx@seu.edu.cn}
  \item Zhenlong Wu, Zhengzhou University, \href{mailto:wuzhenlong2020@zzu.edu.cn}{wuzhenlong2020@zzu.edu.cn}
  \item Cong Yu, Jianghan University, \href{mailto:congy@jhun.edu.cn}{congy@jhun.edu.cn}
  \item Hui Gu, Nanjing Institute of Technology, \href{mailto:gh@njit.edu.cn}{gh@njit.edu.cn}
\end{itemize}

\vspace{1em}
\noindent We thank you for your time and consideration, and look forward to the reviewers' feedback.

\vspace{1em}
\begin{flushright}
Sincerely,\\[1em]
Zhuang~Shao (on behalf of all authors)\\
\href{mailto:shaozhuang@crpower.com.cn}{shaozhuang@crpower.com.cn}
\end{flushright}

\end{document}
