\documentclass[12pt,a4paper]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{booktabs,graphicx,multirow,makecell,bm,enumitem,array}
\usepackage[numbers,comma]{natbib}
\usepackage{hyperref}
\usepackage{setspace}
\onehalfspacing
\setlength{\emergencystretch}{2em}
\usepackage{lineno}
\linenumbers
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}

\newcommand{\R}{\mathbb{R}}\newcommand{\E}{\mathbb{E}}\newcommand{\Prob}{\mathbb{P}}
\newcommand{\calC}{\mathcal{C}}\newcommand{\calU}{\mathcal{U}}\newcommand{\calX}{\mathcal{X}}
\newcommand{\calD}{\mathcal{D}}\newcommand{\calK}{\mathcal{K}}\newcommand{\calS}{\mathcal{S}}
\newcommand{\calO}{\mathcal{O}}\newcommand{\calH}{\mathcal{H}}
\newcommand{\Deltaf}{\Delta f}\newcommand{\Deltag}{\Delta g}
\newcommand{\epsilonKappa}{\epsilon_\kappa}
\newcommand{\sigmatotal}{\sigma_{\mathrm{total}}}
\newcommand{\sigmaGP}{\sigma_{\mathrm{GP}}}\newcommand{\sigmaGPj}[1]{\sigma_{\mathrm{GP},#1}}
\newcommand{\fhat}{\hat{f}}\newcommand{\muGP}{\mu_{\mathrm{GP}}}
\newcommand{\Ahat}{\hat{A}_0}\newcommand{\bhat}{\hat{b}_0}
\DeclareMathOperator*{\argmin}{arg\,min}

\begin{document}

\date{}
\title{A Tunable GP-HOCBF Safety Filter for Supercritical Boiler-Turbine Control under Model Mismatch}

\author{
Zhuang~Shao$^{1,*}$, Lijun~Lei$^{2}$, Peng~Wang$^{3}$, Liang~Zheng$^{2}$, Jie~Zhou$^{2}$\\[1em]
$^{1}$China Resources Power Technology Research Institute Co., Ltd.,\\
\hspace*{1em}Shenzhen 518000, Guangdong Province, China\\
$^{2}$Rundian Energy Science and Technology Co., Ltd.,\\
\hspace*{1em}Zhengzhou 450052, Henan Province, China\\
$^{3}$North China University of Water Resources and Electric Power,\\
\hspace*{1em}Zhengzhou 450046, Henan Province, China\\[0.5em]
$^{*}$Corresponding author: \texttt{shaozhuang@crpower.com.cn},\\
\hspace*{1em}ORCID: 0000-0003-2496-0797
}

\maketitle

\begin{abstract}
Ultra-supercritical boiler-turbine units must keep main steam pressure, separator outlet enthalpy, and turbine power inside protection limits under coal-quality drift, fouling, actuator degradation, and other model mismatch. RoCBF-Net is a tunable safety-filter architecture for a 1000\,MW boiler-turbine measurement and control loop. At each sampling instant, an upstream controller proposes an action; a Gaussian-process (GP)-corrected high-order control barrier function (HOCBF) layer then solves a quadratic program to return the nearest action satisfying the process safety constraints. The implementation propagates GP posterior uncertainty through the HOCBF $\psi$-chain and scales the resulting compositional margin with a scalar factor $\epsilon_\kappa$, so the robustness margin can be commissioned rather than fixed a priori. Evaluation uses a 5th-order nonlinear boiler-turbine benchmark with $\Phi$-scaled control effectiveness, six disturbance scenarios, load-following operation, eight controller/filter variants, and 5 seeds $\times$ 50 episodes $\times$ 500 steps. GP mean correction reduces nominal HOCBF violations by more than 500 times and achieves $\leq0.18\%$ violation in six of seven uncertainty scenarios. Margin calibration is condition-dependent: $\epsilon_\kappa=0$ is sufficient for additive perturbations, $\epsilon_\kappa=0.1$ restores zero violation under state-dependent coupling, and the full theoretical margin $\epsilon_\kappa=1.0$ over-constrains the quadratic program in the tested benchmark. A coupling-strength sweep defines a deployment envelope in which positive margins help at moderate coupling but should be disabled beyond $\gamma\geq1.5$. The JIT-compiled filter runs at about 25\,ms per step, within the 1\,s sampling budget and approximately ten times faster than the implemented SLSQP-based NMPC benchmark. The results position RoCBF-Net as a pre-deployment, commissioning-calibrated safety layer for industrial process-control systems, not as a fixed worst-case robust controller.
\end{abstract}

\textbf{Keywords:} Supercritical boiler-turbine control; safety filter; high-order control barrier function; Gaussian process; model mismatch; robustness margin

\input{sections_mc/intro}
\input{sections_mc/related_work}
\input{sections_mc/methodology}
\input{sections_mc/experimental}
\input{sections_mc/conclusion}

\section*{Statements and Declarations}

\subsection*{Ethical considerations}
Not applicable. This study did not involve human participants, human data, human tissue, or animal experiments.

\subsection*{Consent to participate}
Not applicable.

\subsection*{Consent for publication}
Not applicable.

\subsection*{Declaration of conflicting interests}
The authors declare no potential conflicts of interest with respect to the research, authorship, and/or publication of this article.

\subsection*{Funding}
This work was supported by the Postdoctoral Research Project of China Resources Power Technology Research Institute Co., Ltd. (Internal Project No.\ 374322).

\subsection*{Author contributions}
Zhuang Shao: Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Visualization, Writing -- original draft, Writing -- review \& editing. Lijun Lei: Resources, Supervision, Project administration. Peng Wang: Formal analysis, Writing -- review \& editing. Liang Zheng: Resources, Supervision. Jie Zhou: Investigation, Data curation.

\subsection*{Data availability}
The source code, simulation scripts, trained GP configurations, and plotting scripts required to reproduce the results are available in the \href{https://github.com/VickylastShao/Robust-HOCBF-Safety-Filtering-for-Supercritical-Power-Plants-under-Model-Mismatch}{GitHub repository}. No proprietary plant historian data, human data, or third-party operational datasets were used in this study.

\subsection*{Declaration of generative AI and AI-assisted technologies}
During the preparation of this work, the authors used ChatGPT for language polishing and manuscript formatting. The authors reviewed and edited all content and take full responsibility for the article.

\bibliographystyle{SageV}
\bibliography{refs}

\end{document}
